ATHENS course on Extreme-Value Theory

### 2022-03-16 Practicals/multivariate2022.Rmd
test

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, tidy = FALSE, dev = 'png')
par(mar = c(5, 4, 1, 1) + .1)
WORK = "~/research/enseignement/ATHENS_Cours-Extremes/code/"
setwd(WORK)
options(warn=-1)
```

@@

First, we load the required R packages. 
```{r load packages, message=FALSE}
#library containing the pairwise beta angular measure:
library(BMAmevt)
#library for "3D Visualization Using OpenGL":
library(rgl)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, tidy = FALSE, dev = 'png')
par(mar = c(5, 4, 1, 1) + .1)
#WORK = "~/research/enseignement/ATHENS_Cours-Extremes/code/"
#setwd(WORK)
options(warn=-1)
```

@@

First, we load the required R packages. 
```{r load packages, message=FALSE}
#library containing the pairwise beta angular measure:
library(BMAmevt)
#library for "3D Visualization Using OpenGL":
options(rgl.useNULL = TRUE)
options(rgl.printRglwidget = TRUE)
library(rgl)
```
